\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{array}
\usepackage{xcolor}

\geometry{margin=1in}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
  citecolor=blue
}
\setlength{\parskip}{0.55em}
\setlength{\parindent}{0pt}
\renewcommand{\arraystretch}{1.15}
\setlength{\emergencystretch}{2em}
\Urlmuskip=0mu plus 2mu
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}

\newcommand{\BHSM}{BHSM}
\newcommand{\Bare}{\texttt{BHSM\_BARE\_V1}}
\newcommand{\Dressed}{\texttt{BHSM\_DRESSED\_V1}\allowbreak\texttt{\_CANDIDATE}}
\newcommand{\HT}{\ensuremath{H_T}}
\newcommand{\Omegaf}{\ensuremath{\Omega_f}}
\newcommand{\CommitHash}{\texttt{03039feb14fb4c988edce}\allowbreak\texttt{8453f6ee5b234797eb2}}
\newcommand{\RepoURL}{\url{https://github.com/ncarberry64/Berger-Hopf-Standard-Model}}
\newcommand{\doi}[1]{\href{https://doi.org/#1}{\nolinkurl{#1}}}

\title{The Berger--Hopf Standard Model: A Frozen v1.0 Geometric Reinterpretation of Standard Model Flavor, Couplings, and Generations}
\author{N. Carberry}
\date{BHSM v1.1 technical note package}

\begin{document}
\maketitle

\begin{abstract}
The Berger--Hopf Standard Model (\BHSM) is a no-retuning, alpha-anchored
geometric reinterpretation framework for Standard Model flavor, couplings,
generations, and electroweak-scale structure. This technical note typesets the
frozen v1.0 repository state at commit
\CommitHash{} and tag
\texttt{bhsm-v1.0-freeze}. The frozen construction fixes the Berger anisotropy
$a=\alpha^{-1}/(12\pi^2)$, the universal overlap width $S=1/(4\pi)$, and a
charged-sector mode ledger for charged leptons, up quarks, and down quarks.
Two branches are kept separate: \Bare, the pure alpha-anchored Berger--Hopf
overlap model, and \Dressed, which applies $Z_{\rm virt}^{u,2}=1/2$ only to
$c/t$. The dressed branch remains a candidate, not final canonical adoption.

This note reports frozen prediction ledgers, CKM and Hopf-phase CP screens,
PMNS effective-extension rows, gauge/Higgs/electroweak screens, the finite-basis
\HT{} proxy gap audit, scalar/topographic scaffold status, fixed tolerance
bands, and falsification criteria F1--F9. It does not claim a first-principles
derivation of the Standard Model, an analytic proof of the full \HT{}
no-extra-light-state theorem, or a proof of scalar decoupling from the full
action.
\end{abstract}

\section{Introduction}

\BHSM{} means Berger--Hopf Standard Model. It is used here as a frozen,
no-retuning geometric reinterpretation framework for Standard Model flavor,
couplings, generations, and electroweak-scale structure. The v1.0 freeze is not
a new fit performed inside this manuscript. It is the documented repository
state at commit \CommitHash{}, tag
\texttt{bhsm-v1.0-freeze}, where the test suite passed with 269 tests at the
freeze and 278 tests on the current paper branch.

The Standard Model remains the reference low-energy quantum field theory for
the gauge and matter ledger used here. \BHSM{} is not presented as replacing the
Standard Model. It is a no-retuning geometric reinterpretation framework whose
outputs are compared against standard phenomenological ledgers and reference
quantities.

The core claim discipline is conservative. Hypercharge and anomaly checks are
ledger-level and test-backed. Flavor outputs are internal-rule screens tied to
the supplied mode ledger and overlap rule. Gauge and electroweak outputs are
matching screens. The \HT{} and scalar/topographic sectors remain proxy or
scaffold audits. The dressed branch is an adoption candidate, not a final
canonical model.

\section{Repository and Reproducibility}

This technical note is assembled from the private development repository for
the Berger--Hopf Standard Model project. It is a manuscript artifact on the
paper branch and does not alter the frozen model.

\begin{longtable}{@{}L{0.28\linewidth}L{0.66\linewidth}@{}}
\toprule
Item & Value \\
\midrule
Repository & \RepoURL{} \\
Frozen tag & \texttt{bhsm-v1.0-freeze} \\
Model freeze commit & \CommitHash{} \\
Manuscript branch & \texttt{bhsm-v1.1-paper} \\
Freeze tests & \texttt{269 passed} \\
Paper-branch QA tests & \texttt{278 passed} \\
\bottomrule
\end{longtable}

Reproducibility command:
\begin{verbatim}
python -m pytest -q
\end{verbatim}

\section{Framework and Frozen Configuration}

The v1.0 freeze fixes the alpha-anchored Berger geometry and universal overlap
width before any manuscript scoring.

\begin{table}[h]
\centering
\caption{Frozen constants.}
\small
\begin{tabular}{@{}L{0.25\linewidth}L{0.37\linewidth}L{0.27\linewidth}@{}}
\toprule
Quantity & Frozen value & Status \\
\midrule
Berger anisotropy & $a=\alpha^{-1}/(12\pi^2)=1.157054135733433$ & alpha-anchored canonical geometry \\
Universal overlap width & $S=1/(4\pi)=0.07957747154594767$ & frozen overlap width \\
\bottomrule
\end{tabular}
\end{table}

The alpha-anchored geometry is selected by the theory-side rule recorded in the
model card: the \BHSM{} scale sector contains
$\epsilon_\alpha=\alpha^{-1}/(12\pi^2)-1$. It is not selected by residual
minimization.

\begin{table}[h]
\centering
\caption{Fixed charged-sector mode ledger.}
\begin{tabular}{@{}llll@{}}
\toprule
Sector & Heavy & Middle & Light \\
\midrule
charged leptons & $(0,0)$ & $(5,2)$ & $(9,3)$ \\
up quarks & $(0,0)$ & $(6,0)$ & $(10,1)$ \\
down quarks & $(0,0)$ & $(6,3)$ & $(8,2)$ \\
\bottomrule
\end{tabular}
\end{table}

The Hopf charge is $q=k-2j$. Charged-sector ratios use the frozen overlap rule
\[
  \frac{m_i}{m_3}=\exp[-S\lambda_{k,j}],
\]
with the Berger scalar spectrum proxy
\[
  \lambda_{k,j}(a)=a^2(k-2j)^2+2((2j+1)k-2j^2).
\]

\section{Gauge and Field Ledger}

The repository audits the Standard Model gauge and matter ledger as a
conditional ledger within the admitted \BHSM{} framework. The manuscript does
not claim a derivation of the Standard Model from pure geometry alone. It
records the tested statement that the admitted chiral representation pattern,
Higgs-selected $U(1)$, Yukawa invariance, and anomaly cancellation reproduce
the anomaly-free Standard Model ledger conditionally.

\section{Flavor Prediction Ledger}

\subsection{\Bare{} branch}

\begin{table}[h]
\centering
\caption{Frozen \Bare{} charged-sector and CKM outputs.}
\small
\begin{tabular}{@{}lll@{}}
\toprule
Quantity & Value & Status \\
\midrule
$\mu/\tau$ & $0.05985960910845228$ & frozen output \\
$e/\tau$ & $0.00028830990267827904$ & frozen output \\
$c/t$ & $0.008310500554068288$ & scheme-sensitive comparison \\
$u/t$ & $1.2690463017606151\times10^{-5}$ & scheme-sensitive comparison \\
$s/b$ & $0.021933971495439474$ & scheme-sensitive comparison \\
$d/b$ & $0.0011165200546001757$ & scheme-sensitive comparison \\
$\sin\theta_{12}$ & $0.2256184580048353$ & CKM screen \\
$\sin\theta_{23}$ & $0.04386794299087895$ & CKM screen \\
$\sin\theta_{13}$ & $0.0035623676140463315$ & CKM screen \\
\bottomrule
\end{tabular}
\end{table}

\subsection{\Dressed{} branch}

\begin{table}[h]
\centering
\caption{Frozen \Dressed{} changes relative to \Bare{}.}
\small
\begin{tabular}{@{}L{0.13\linewidth}L{0.25\linewidth}L{0.25\linewidth}L{0.12\linewidth}@{}}
\toprule
Quantity & \Bare{} & \Dressed{} & Changed \\
\midrule
$c/t$ & $0.008310500554068288$ & $0.004155250277034144$ & yes \\
$u/t$ & $1.2690463017606151\times10^{-5}$ & $1.2690463017606151\times10^{-5}$ & no \\
$s/b$ & $0.021933971495439474$ & $0.021933971495439474$ & no \\
$d/b$ & $0.0011165200546001757$ & $0.0011165200546001757$ & no \\
$\sin\theta_{13}$ & $0.0035623676140463315$ & $0.0035623676140463315$ & no \\
\bottomrule
\end{tabular}
\end{table}

The dressed branch changes only $c/t$ using $Z_{\rm virt}^{u,2}=1/2$ for the
pure-fiber middle up mode $(6,0)$. It leaves $u/t$, CKM $\sin\theta_{13}$,
down-sector ratios, lepton ratios, gauge outputs, Higgs/electroweak outputs,
\HT{}, and scalar outputs unchanged. It remains a candidate, not final
canonical adoption.

\section{CKM and CP Structure}

The CKM angle screens use frozen canonical \BHSM{} ratios:
\[
  \sin\theta_{12}\approx\sqrt{d/s},\qquad
  \sin\theta_{23}\approx 2(s/b),\qquad
  \sin\theta_{13}\approx\sqrt{u/t}.
\]
The Hopf-phase CP screen computes
\[
  \delta_{\rm CKM}^{\rm BHSM}=\Delta q\sqrt{S},
\]
with $\Delta q$ from the light up/down Hopf charges. The frozen branch reports
\[
  \delta_{\rm CKM}=1.1283791670955126,\qquad
  J_{\rm CKM}=3.1011702945437805\times10^{-5}.
\]
The phase is a model-output screen, not an empirical insertion.

\section{Gauge, Higgs, and Electroweak Screens}

The gauge coupling screens are interpreted as electroweak-scale matching
conditions:
\[
  \alpha_1=\frac{1}{6\pi^2},\qquad
  \alpha_2=\frac{1}{3\pi^2},\qquad
  \alpha_3\approx\frac{7}{6\pi^2},
\]
\[
  \sin^2\theta_W=\frac{3}{13},\qquad
  \alpha_{\rm EM}^{-1}=13\pi^2.
\]
The Higgs/electroweak screen uses
\[
  \epsilon_\alpha=\alpha^{-1}/(12\pi^2)-1,\qquad
  v=2\sqrt{2}E_P\exp[-4\pi^2-\epsilon_\alpha/(4\pi^2)].
\]
Precision QCD/RG matching remains open; the one-loop and running scaffolds are
comparison tools, not completed high-precision threshold matching.

\section{\texorpdfstring{$H_T$}{H\_T} Gap and Scalar Sector}

The no-extra-light-state condition is audited through proxy and finite-basis
scaffolds. The target is
\[
  H_T|_{\mathcal H_\perp}\ge (4\pi^2v)^2.
\]
The dimensionless Hopf target is $\mu_H=64\pi^5$. The current repository
contains proxy spectral-gap, positive-semidefinite profile, Level 2 finite-basis
twisted Dirac, lower-bound, and basis-convergence audits. The \HT{} theorem
remains proxy/scaffold audited, not analytically proven.

Scalar decoupling remains scaffold audited. Scalar/topographic decoupling remains open
at the full action level. The Standard-Model limit requires exactly one light
Higgs projection and no unscreened light direct-coupled scalar. Full scalar
decoupling from the action remains open.

\section{Bare vs Dressed Branches}

The bare branch is the pure alpha-anchored Berger--Hopf overlap model. The
dressed-candidate branch is the same frozen model except for the local
virtual-environment factor $Z_{\rm virt}^{u,2}=1/2$ applied only to $c/t$. The
branches are separate ledger entries. The dressed branch is an adoption
candidate, not final canonical adoption.

\section{Falsification Ledger}

\small
\begin{longtable}{@{}L{0.06\linewidth}L{0.66\linewidth}L{0.20\linewidth}@{}}
\caption{Frozen falsification criteria.}\\
\toprule
ID & Criterion & Status \\
\midrule
\endfirsthead
\toprule
ID & Criterion & Status \\
\midrule
\endhead
F1 & If alpha-anchored $a$ cannot be derived from the internal action, \BHSM{} geometry weakens. & open proof obligation \\
F2 & If $\Omega_f$ cannot be derived from the twisted Dirac/bundle action, mass hierarchy predictions remain unsupported. & open proof obligation \\
F3 & If scheme-consistent quark ratios disagree beyond fixed tolerance bands, \BHSM{} flavor mapping fails or must be revised. & falsifiable numerical branch \\
F4 & If canonical \BHSM{} $V_{us}$, $V_{cb}$, $V_{ub}$, $\delta$, and $J$ fail outside fixed tolerances, \BHSM{} flavor mapping is falsified or constrained. & falsifiable numerical branch \\
F5 & If neutrino ordering, octant, or phase decisively contradict \BHSM{} effective-extension outputs, the neutrino branch fails. & effective-extension branch \\
F6 & If the full twisted Dirac/\HT{} spectrum produces extra light states below $4\pi^2v$, the SM-equivalent \BHSM{} mapping fails. & open spectral theorem \\
F7 & If unscreened light scalar/topographic modes remain, \BHSM{} fails as a Standard-Model-equivalent low-energy theory. & open action-level proof \\
F8 & If higher-loop/threshold RG matching moves coupling agreement away from the electroweak scale beyond tolerance, the coupling branch weakens. & open RG matching \\
F9 & Any post-freeze adjustment of $a$, $S$, modes, or $Z_{\rm virt}$ based on residuals invalidates the v1.0 prediction set. & freeze constraint \\
\bottomrule
\end{longtable}

\begin{table}[h]
\centering
\caption{Fixed tolerance bands.}
\small
\begin{tabular}{@{}ll@{}}
\toprule
Class & Tolerance \\
\midrule
exact status & pass/fail \\
gauge couplings & $0.01$ \\
Higgs/electroweak $v$ & $0.01$ \\
Higgs mass zeroth-order & $0.02$ \\
charged lepton ratios & $0.25$ \\
quark ratios, scheme-aware & $0.25$ \\
quark ratios, otherwise & scheme-sensitive \\
CKM angles & $0.10$ \\
CKM CP/Jarlskog & $0.10$ \\
PMNS effective & $0.05$ \\
\HT{} gap & binary pass/fail \\
scalar decoupling & binary scaffold pass/fail \\
\bottomrule
\end{tabular}
\end{table}

\section{Limitations and Open Proof Obligations}

\small
\begin{longtable}{@{}L{0.30\linewidth}L{0.60\linewidth}@{}}
\caption{Open proof obligations.}\\
\toprule
Topic & Current limitation \\
\midrule
\endfirsthead
\toprule
Topic & Current limitation \\
\midrule
\endhead
\HT{} spectrum & Proxy/scaffold audited, not analytically proven; full twisted Dirac spectrum remains open. \\
Scalar decoupling & Scaffold audited; full action-level scalar/topographic decoupling remains open. \\
Boundary operators $\Omega_f$ & Action-linked, not fully action-derived from the twisted Dirac/bundle action. \\
Precision QCD/RG matching & Higher-loop, threshold-aware, scheme-consistent matching remains open. \\
Dressed branch & Candidate only; not final canonical adoption. \\
PMNS sector & Effective-extension screen, not a minimal Standard Model prediction. \\
\bottomrule
\end{longtable}

The no-retuning rule remains central: changing $a$, $S$, the supplied mode
ledger, tolerance bands, or $Z_{\rm virt}$ based on residuals invalidates the
frozen package.

\section{Publication Declarations}

\textbf{Funding.} No external funding is declared unless otherwise specified by
the author.

\textbf{Conflicts of interest.} None declared unless otherwise specified by the
author.

\textbf{Data availability.} No new observational data are introduced. Code and
repository availability are by author decision.

\textbf{Code availability.} The \BHSM{} v1.0 freeze is identified by tag
\texttt{bhsm-v1.0-freeze}. Its commit is \CommitHash{}.

\textbf{AI/tool assistance.} Manuscript and repository organization used
AI-assisted drafting/coding support; scientific responsibility remains with the
author.

\section{Conclusion}

The frozen \BHSM{} v1.0 repository defines a reproducible no-retuning
prediction and falsification package for a Berger--Hopf reinterpretation of
Standard Model flavor, couplings, generations, and electroweak-scale structure.
This v1.1 paper branch turns that package into a submission-oriented technical
note without changing the frozen model. The next technical work remains
action-level derivation of $\Omega_f$, full analytic \HT{} spectral
computation, scalar/topographic decoupling from the full action, and precision
QCD/RG matching.

\section{References}

\begin{enumerate}
\item S. Navas et al. (Particle Data Group), ``Review of Particle Physics,''
\textit{Physical Review D} \textbf{110}, 030001 (2024).
DOI: \doi{10.1103/PhysRevD.110.030001}.
\item S. L. Glashow, ``Partial-symmetries of weak interactions,''
\textit{Nuclear Physics} \textbf{22}, 579--588 (1961).
DOI: \doi{10.1016/0029-5582(61)90469-2}.
\item S. Weinberg, ``A Model of Leptons,'' \textit{Physical Review Letters}
\textbf{19}, 1264--1266 (1967). DOI: \doi{10.1103/PhysRevLett.19.1264}.
\item C. D. Froggatt and H. B. Nielsen, ``Hierarchy of quark masses, Cabibbo
angles and CP violation,'' \textit{Nuclear Physics B} \textbf{147}, 277--298
(1979). DOI: \doi{10.1016/0550-3213(79)90316-X}.
\item N. Cabibbo, ``Unitary Symmetry and Leptonic Decays,''
\textit{Physical Review Letters} \textbf{10}, 531--533 (1963).
DOI: \doi{10.1103/PhysRevLett.10.531}.
\item M. Kobayashi and T. Maskawa, ``CP-Violation in the Renormalizable Theory
of Weak Interaction,'' \textit{Progress of Theoretical Physics} \textbf{49},
652--657 (1973). DOI: \doi{10.1143/PTP.49.652}.
\item Z. Maki, M. Nakagawa, and S. Sakata, ``Remarks on the Unified Model of
Elementary Particles,'' \textit{Progress of Theoretical Physics} \textbf{28},
870--880 (1962). DOI: \doi{10.1143/PTP.28.870}.
\item S. M. Bilenky and S. T. Petcov, ``Massive neutrinos and neutrino
oscillations,'' \textit{Reviews of Modern Physics} \textbf{59}, 671--754
(1987). DOI: \doi{10.1103/RevModPhys.59.671}.
\item A. Connes, \textit{Noncommutative Geometry}, Academic Press (1994).
ISBN: \texttt{0-12-185860-X}.
\item W. D. van Suijlekom, \textit{Noncommutative Geometry and the Standard
Model of Elementary Particle Physics}, Springer (2015).
DOI: \doi{10.1007/978-94-017-9162-5}.
\item J. M. Overduin and P. S. Wesson, ``Kaluza-Klein gravity,''
\textit{Physics Reports} \textbf{283}, 303--378 (1997).
DOI: \doi{10.1016/S0370-1573(96)00046-4}.
\item C. P. Burgess, ``An Introduction to Effective Field Theory,''
\textit{Annual Review of Nuclear and Particle Science} \textbf{57}, 329--362
(2007). DOI: \doi{10.1146/annurev.nucl.56.080805.140508}.
\item K. G. Chetyrkin, J. H. Kuhn, and M. Steinhauser, ``RunDec: A Mathematica
package for running and decoupling of the strong coupling and quark masses,''
\textit{Computer Physics Communications} \textbf{133}, 43--65 (2000).
DOI: \doi{10.1016/S0010-4655(00)00155-7}.
\item G. K. Sandve, A. Nekrutenko, J. Taylor, and E. Hovig, ``Ten Simple Rules
for Reproducible Computational Research,'' \textit{PLOS Computational Biology}
\textbf{9}(10), e1003285 (2013).
DOI: \doi{10.1371/journal.pcbi.1003285}.
\end{enumerate}

\end{document}

